The {\em Diff} MILP model and PCA for \\ {\em real-time} DNN robustness certification

### 2025-12-04 CAV 2026/global.tex
update the definition

TODO: DEF OF BOUNDS IN VHAGAR. CALL BOUNDS 
$\alpha^{\text{perturb}}_{C,D}$, to compute the perturbation necessary to switch an image classified as $C$ into an image classified as $D$.
Notice that $\alpha^{\text{perturb}}_{C,D}$ is not symetrical, while 
$\beta^{\text{perturb}}_{C,D}$ is.

>>>>

The bounds in Vhagar, 
$\alpha^{\text{perturb}}_{C,D}$, to compute the perturbation necessary to switch an image classified as $C$ into an image classified as $D$. The formal definition, \begin{align*}
	\alpha^{\text{perturb}}_{C,D} &= \max_{|I-I'| \leq \text{perturb}} (x_C-\max_{E\neq C}x_E) \\
	&\text{s.t. }  (x'_D-\max_{E\neq D}x'_E)\geq 0
\end{align*}
Notice that $\alpha^{\text{perturb}}_{C,D}$ is not symetrical, while 
$\beta^{\text{perturb}}_{C,D}$ is.
